---
title: "An Excerpt of the Krummhörn database (version KH33b)"
author: "Johannes Johow"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{kh33}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This short report documents the function `built_kh()` to create a sample from the _Krummhörn_ database in its most recent version (''KH33b'') as well as some  `kinlab::` utilities useful in visualisation and modelling during the ecological analysis of kin networks provided by historical data. It purposes three main goals:

- Create required data structures for given pedigrees
- Graphical tools to display relatedness, survival and fertility 
- Multistate modelling of individual pedigrees

## Vignette Info


## Data Import

The `built_kh` function is able to compile a given number (`n`) of pedigrees and will save all relevant data to local files. 

## Figures

`kinlab::plot_pedigree(x, evdat, ped)` plots the pedigree  pedigree and will save all relevant data to local files. 

```{r}
kh.data::built_kh(
  source_path = "/home/johow/Dropbox/db/kh", 
  local_path="/home/johow/tmp/kh.data/data", 
  n = 32, silent=TRUE, set_seed=13)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(kh.data::kh_geo[[1]], 10))
```


```{r, echo=FALSE, fig.width=7, fig..height=7}

kinlab::plot_pedigree(as.numeric( names(kh.data::kh_ped)[1]), kinlab::as_date(kh.data::kh_mat[names(kh.data::kh_ped)[1],2,1]), as.data.frame(kh.data::kh_ind),  kh.data::kh_ped[[1]],
kh.data::kh_mat, cex = 0.2)
```


```{r, echo=FALSE, fig.width=7}
print(
kinlab::plot_kinmap(id=as.numeric( names(kh.data::kh_ped)[1]),
                      evdat= kinlab::as_date(kh.data::kh_mat[names(kh.data::kh_ped)[1],2,1]),
                      list_kin=kh.data::kh_kin,
                      list_geo=kh.data::kh_geo,
                      my_map=kh.data::kh_geo[[2]][[1]],
                      spit_results=TRUE,
                      throw_plots=FALSE))
```


```{r, echo=FALSE, fig.width=7}


df_xs <- data.frame(momid = unique(kh.data::kh_ind$momid[kh.data::kh_ind$momid>0]), tmp = NA)
df_xs$twinmother <- ifelse(df_xs$momid %in% kinlab::get_twinmothers(kh.data::kh_ind, var_bdate="bdate", var_mother="momid"), 1, 0)

kinlab::plot_rrv(df=df_xs,
                 momid = "momid",
                 var="twinmother",
                 kh.data::kh_ind, kh.data::kh_mat, kh.data::kh_mat,
                 categories=NULL,
                 action = "make.plot",
                 y.lim=NULL)

```

